APPM report - Draft

### 2022-11-03 paper_version/main.tex
minor change

To clarify the notation, in three dimensions the primal mesh $\mathcal{M}$ is a cell complex defined by the set of elements $\{P, L, A, V\}$\footnote{The notation here is a bit floppy. $P, L, A, V$ can refer to a single element or a set of elements.} denoting \emph{vertices, edges, faces} and \emph{cells} respectively. In the same way, the dual mesh $\Tilde{\mathcal{M}}$ is defined by $\{\Tilde{P}, \Tilde{L}, \Tilde{A}, \Tilde{V}\}$. Elements of two meshes are associated with bijective mappings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.})$ corresponds to $\Tilde{V}(V \text{ resp.})$ where it lies and $L(\Tilde{L} \text{ resp.})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.})$. According to their dimensions, vertices, edges, faces and cells are also termed 0-dim, 1-dim, 2-dim and 3-dim elements respectively. Meanwhile, we denote by $N_\ast, \ast \in \{P, \Tilde{P}, L, \Tilde{L},A, \Tilde{A},V, \Tilde{V}\}$ the total number of elements in $\mathcal{M}, \Tilde{\mathcal{M}}$.

@@

\subsubsection{Orientation and Incidence Matrices}
Each geometric element in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an \emph{internal orientation}\footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite{tonti_2002}.}. The notion is sketched in Fig. \ref{fig:orientation}. For the elements of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal elements according to the bijective mappings, i.e. edges penetrate faces.

>>>>

To clarify the notation, in three dimensions the primal mesh $\mathcal{M}$ is a cell complex defined by the set of elements $\{P, L, A, V\}$\footnote{The notation here is a bit floppy. $P, L, A, V$ can refer to a single element or a set of elements.} denoting \emph{vertices, edges, faces} and \emph{cells} respectively. In the same way, the dual mesh $\Tilde{\mathcal{M}}$ is defined by $\{\Tilde{P}, \Tilde{L}, \Tilde{A}, \Tilde{V}\}$. Elements of two meshes are associated with bijective pairings $P \leftrightarrow \Tilde{V}$, $L \leftrightarrow \Tilde{A}$, $A \leftrightarrow \Tilde{L}$ and $V \leftrightarrow \Tilde{P}$ which arise in a very natural way: $P(\Tilde{P} \text{ resp.})$ corresponds to $\Tilde{V}(V \text{ resp.})$ where it lies and $L(\Tilde{L} \text{ resp.})$ penetrates its corresponding $\Tilde{A}(A \text{ resp.})$. According to their dimensions, vertices, edges, faces and cells are also termed 0-dim, 1-dim, 2-dim and 3-dim elements respectively. Meanwhile, we denote by $N_\ast, \ast \in \{P, \Tilde{P}, L, \Tilde{L},A, \Tilde{A},V, \Tilde{V}\}$ the total number of elements in $\mathcal{M}, \Tilde{\mathcal{M}}$.

@@

\subsubsection{Orientation and Incidence Matrices}
Each geometric element in the primal mesh $\mathcal{M}$ is (arbitrarily) endowed with an \emph{internal orientation}\footnote{This notion should not be aliased with \emph{inner orientation}, which has a slightly different definition, see \cite{tonti_2002}.}. The notion is sketched in Fig. \ref{fig:orientation}. For the elements of the dual mesh $\Tilde{\mathcal{M}}$, we set their internal orientations to be aligned with their corresponding primal elements according to the bijective pairings, i.e. edges penetrate faces.
